---
title: "Health Exams in Vietnam"
author: "Gabriel Krotkov"
date: "2023-12-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
theme_set(theme_bw())
library(gridExtra)
data <- read_csv("vietnam-health.csv")
# code response factor levels
data$RecPerExam <- factor(data$RecPerExam, levels = c("unknow", "less12", "b1224", "g24"))
```

\newpage

# Data

The data are survey responses from the cities of Hanoi and Hung Yen, Vietnam focused on "secondary schools, hospitals, companies, government agencies and randomly selected households"

## Interpreting 

# EDA

## Information Ratings

```{r}
suff_plot <- ggplot(data, aes(x = SuffInfo)) + 
    geom_bar(fill = "purple") + 
    labs(title = "Sufficiency Ratings", 
         x = "Information Sufficiency")

attract_plot <- ggplot(data, aes(x = AttractInfo)) + 
    geom_bar(fill = "purple") + 
    labs(title = "Attractiveness Ratings", 
         x = "Information Attractiveness")

impress_plot <- ggplot(data, aes(x = ImpressInfo)) + 
    geom_bar(fill = "purple") + 
    labs(title = "Impressiveness Ratings", 
         x = "Information Impresiveness")

popular_plot <- ggplot(data, aes(x = PopularInfo)) + 
    geom_bar(fill = "purple") + 
    labs(title = "Popularity Ratings", 
         x = "Information Popularity")


grid.arrange(suff_plot, attract_plot, impress_plot, popular_plot, 
             nrow = 2)

tukey_summaries <- rbind(quantile(data$SuffInfo), quantile(data$AttractInfo), 
                         quantile(data$ImpressInfo), quantile(data$PopularInfo))
rownames(tukey_summaries) <- c("Sufficiency", "Attractiveness", 
                               "Impressiveness", "Popularity")

knitr::kable(tukey_summaries)
```

People tend to rate the Sufficiency, Attractiveness, Impressiveness, and Popularity of information received from checkups at a 3/5 on average, with a similar distribution for each variable. For Attractiveness in particular there appears to be a slight asymmetry (with 2/5 getting nearly as high a rating as 3/5), but in general the four plots all agree on the distribution of the response. We can also see from the table of quantiles that the 5-number summaries for all the variables are identical. Taken together, I am comfortable using Impressiveness as a proxy for all the response variables, since its distribution seems to be the closest to the average of all the other distributions. 

We will also explore some metrics of checkup quality to get an indicator for how quality current checkups are.

```{r}
reliability_plot <- ggplot(data, aes(x = Reliability)) + 
    geom_bar(fill = "purple") + 
    labs(title = "Reliability Rating", 
         x = "Reliability")

assurance_plot <- ggplot(data, aes(x = Assurance)) + 
    geom_bar(fill = "purple") + 
    labs(title = "Assurance Rating", 
         x = "Assurance")

empathy_plot <- ggplot(data, aes(x = Empathy)) + 
    geom_bar(fill = "purple") + 
    labs(title = "Empathy Rating", 
         x = "Empathy")

tangibles_plot <- ggplot(data, aes(x = Tangibles)) + 
    geom_bar(fill = "purple") + 
    labs(title = "Tangibles Rating", 
         x = "Tangibles")

grid.arrange(reliability_plot, assurance_plot, empathy_plot, tangibles_plot, 
             nrow = 2)
```

For key metrics of care qualtiy, we can see that on average patients rate their care reasonably highly. There is clear leftward skew in each of the plots, and ratings of 1 and 2 are relatively rare. It seems like the performance metric with the most opportunity for the Ministry to improve is `empathy`, since while a very high number of patients gave a score of 5/5, the combined count for scores 1/5 and 2/5 is the highest of the variables we consider here.

## Factors Influencing Checkup Consistency

Among reliability, empathy, tangibles, and assurance, we are interested in finding the variables that most impact checkup consistency. To investigate this, we can plot each of the variables of interest across the different levels of checkup recency.

```{r}
reliability_plot <- ggplot(data, aes(x = RecPerExam, y = Reliability)) + 
    geom_violin(fill = "darkorange", alpha = 0.6) + 
    geom_boxplot(fill = "purple", alpha = 0.6) + 
    labs(title = "Reliability across exam consistencies")

empathy_plot <- ggplot(data, aes(x = RecPerExam, y = Empathy)) + 
    geom_violin(fill = "darkorange", alpha = 0.6) + 
    geom_boxplot(fill = "purple", alpha = 0.6) + 
    labs(title = "Empathy across exam consistencies")

tangibles_plot <- ggplot(data, aes(x = RecPerExam, y = Tangibles)) + 
    geom_violin(fill = "darkorange", alpha = 0.6) + 
    geom_boxplot(fill = "purple", alpha = 0.6) + 
    labs(title = "Tangibles across exam consistencies")

assurance_plot <- ggplot(data, aes(x = RecPerExam, y = Assurance)) + 
    geom_violin(fill = "darkorange", alpha = 0.6) + 
    geom_boxplot(fill = "purple", alpha = 0.6) + 
    labs(title = "Assurance across exam consistencies")

grid.arrange(reliability_plot, assurance_plot, empathy_plot, tangibles_plot, 
             nrow = 2)
```

We can see from these plots that it appears that the biggest and most consistent difference in distribution appears to be across the `Empathy` variable - the mean appears to clearly take a different value among lower empathy values, compared to less clear effects along the other variables.

## Impact of Health Issues

```{r}
mosaicplot(table(data$RecPerExam, 
                 data$StabHthStt))
```
From the mosaic plot, it appears that health issues among the respondants and their families are not correlated to the response variable.

# Instructions for statistical analyses

Create linear models testing the hypotheses created in the above two parts, including interaction terms for testing the interaction effects. 
