---
title: "Health Exams in Vietnam"
author: "Gabriel Krotkov, Zachary Strennen"
date: "2023-12-13"
output: pdf_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
theme_set(theme_bw())
library(gridExtra)
library(leaps)
library(reshape2)
load("data.rda")
```

# Executive Summary

# Introduction

@TODO Clearly outline the Ministry's research questions

# Data

The data were collected by public health researchers in Vietnam in order to determine what obstacles were preventing widespread us of regular check-ups. The researchers conducted interviews in Hanoi and Hung Yen Vietnam and primarily traveled to secondary schools, hospitals, companies, government agencies and randomly selected households in Hanoi. The interviews were in person and lasted about 10-15 minutes. Out of the 2,479 people approached, there were 2,068 valid responses added to the data.

For two of the key research questions in this report, the variable we will choose as the response variable is `RecPerExam`, a measure of how long it has been since the respondent last had a checkup *without* a catalyzing health event motivating them to go to the doctor. For this variable, 516 of the 2068 respondents had a value of `unknown`. There are many possible explanations for not knowing how long it has been since your most recent personal checkup, some of which cut against each other when it comes to interpreting the analysis. For example, if a respondent reported "unknown" because it has been so long they cannot remember, that has a very different impact on what inferences we should draw about that respondent than if they reported "unknown" because they were unsure if it was 11 months ago or 12 months ago. Since we don't have any additional information about the reasoning behind the `unknown` status, we will remove all respondents who reported `unkown` from the dataset for the remainder of the analysis.

As part of the data cleaning, we removed all respondents whose reason for getting a checkup was because their employer or insurance requested that they do. These semi-compulsory exams are not useful information for getting at the Ministry's fundamental question - how do we drive more voluntary checkups? Removing such entries allows us to narrow our focus to those who are not immediately pressured to get a check-up.

# Exploratory Data Analysis

## Information Ratings

To answer the Ministry's first research question, we can investigate respondents' ratings of key information features visually.

```{r}
suff_plot <- ggplot(data, aes(x = SuffInfo)) + 
    geom_bar(fill = "purple", color = "black") + 
    labs(title = "Sufficiency Ratings", 
         x = "Information Sufficiency")

attract_plot <- ggplot(data, aes(x = AttractInfo)) + 
    geom_bar(fill = "purple", color = "black") + 
    labs(title = "Attractiveness Ratings", 
         x = "Information Attractiveness")

impress_plot <- ggplot(data, aes(x = ImpressInfo)) + 
    geom_bar(fill = "purple", color = "black") + 
    labs(title = "Impressiveness Ratings", 
         x = "Information Impresiveness")

popular_plot <- ggplot(data, aes(x = PopularInfo)) + 
    geom_bar(fill = "purple", color = "black") + 
    labs(title = "Popularity Ratings", 
         x = "Information Popularity")

grid.arrange(suff_plot, attract_plot, impress_plot, popular_plot, 
             nrow = 2)

rm(suff_plot, attract_plot, impress_plot, popular_plot)
```

People tend to rate the Sufficiency, Attractiveness, Impressiveness, and Popularity of information received from checkups at a 3/5 on average, with a similar distribution for each variable. For Attractiveness in particular there appears to be a slight asymmetry (with 2/5 getting nearly as high a rating as 3/5), but in general the four plots all agree on the distribution of the response.

```{r, fig.height = 3}
summ_stat <- data.frame(mean = c(mean(data$SuffInfo), 
                                 mean(data$AttractInfo), 
                                 mean(data$ImpressInfo), 
                                 mean(data$PopularInfo)), 
                        stdev = c(sd(data$SuffInfo), sd(data$AttractInfo), 
                                  sd(data$ImpressInfo), sd(data$PopularInfo)))

rownames(summ_stat) <- c("Sufficiency", "Attractiveness", 
                         "Impressiveness", "Popularity")

knitr::kable(summ_stat)

cidx <- which(colnames(data) %in% c("SuffInfo", "AttractInfo", 
                                    "ImpressInfo", "PopularInfo"))

sd_scores <- apply(data[, cidx], MARGIN = 1, sd)

avg_plot <- ggplot(data, aes(x = (SuffInfo + AttractInfo + 
                                      ImpressInfo + PopularInfo) / 4)) + 
    geom_histogram(bins = 8, fill = "purple", color = "black") + 
    labs(title = "Average plot", 
         subtitle = "Across Info Metrics",
         x = "Avg Info Rating")

sd_info_plot <- ggplot(data.frame(sd_scores), aes(x = sd_scores)) + 
    geom_histogram(bins = 8, fill = "purple", color = "black") + 
    labs(title = "Respondent Standard Deviation",
         subtitle = "Across Info Metrics",
         x = "Respondent Standard Deviation", y = "Count")

grid.arrange(avg_plot, sd_info_plot, nrow = 1)

rm(avg_plot, sd_info_plot, summ_stat)
```

We can also see from the table of summary statistics that the means and standard deviations of the variables are nearly identical. This indicates in general that the average respondent is generally either pleased or not pleased with the information given to them in a checkup, and doesn't tend to distinguish between the Sufficiency, Attractiveness, Impressiveness or Popularity of the information. To further bolster this point, the average standard deviation of the respondent's scores across each information metric is a very right skewed and left centered metric, indicating that respondents' scores do not vary much across the different metrics. Taken together with the close matching of the average metric plot and the Information Impressiveness plot, it is a safe simplification to use Information Impressiveness as a proxy for the respondent's overall satisfaction with information provided at a checkup.

We will also explore some metrics of checkup quality to get an indicator for how quality current checkups are, as per the Ministry's questions.

```{r}
cidx <- which(colnames(data) %in% c("Tangibles", "Reliability", "Respon", 
                                    "Assurance", "Empathy"))
quality <- melt(data[, cidx])

ggplot(quality, aes(x = value, fill = variable)) + 
    geom_density(alpha = 0.3) + 
    facet_wrap(~variable)
```

For key metrics of care quality, we can see that on average patients rate their care reasonably highly. There is clear leftward skew in each of the plots, and ratings of 1 and 2 are relatively rare. It seems like the performance metric with the most opportunity for the Ministry to improve is `empathy`, since while a very high number of patients gave a score of 5/5, the combined count for scores 1/5 and 2/5 is the highest of the variables we consider here.

```{r, echo=FALSE}
# Does the respondent believe check-ups are a waste of money?
barplot1 <-
    data %>% ggplot(aes(x = Wstmon, y = after_stat(count), fill = RecPerExam)) +
    geom_bar(position = 'dodge') +
    labs(x="",
         y="Frequency",
         title = "Are check-ups a waste\nof money?",
         fill="Months since\nlast check-up")

# Is the respondent afraid of check-ups because they're afraid of discovering a disease?
barplot2 <-
    data %>% ggplot(aes(x = DiscDisease, y = after_stat(count), fill = RecPerExam)) +
    geom_bar(position = 'dodge') +
    labs(x="",
         y="Frequency",
         title = "Are you afriad of discovering\na new disease?",
         fill="Months since\nlast check-up")

# Does the respondent have little faith in the quality of medical service?
barplot3 <-
    data %>% ggplot(aes(x = Lessbelqual, y = after_stat(count), fill = RecPerExam)) +
    geom_bar(position = 'dodge') +
    labs(x="",
         y="Frequency",
         title = "Do you have little faith in\nthe quality of medical\nservice?",
         fill="Months since\nlast check-up")

# Does the respondent believe check-ups are not urgent or important?
barplot4 <-
    data %>% ggplot(aes(x = NotImp, y = after_stat(count), fill = RecPerExam)) +
    geom_bar(position = 'dodge') +
    labs(x="",
         y="Frequency",
         title = "Do you believe check-ups are\nnot urgent or important?",
         fill="Months since\nlast check-up")

# Does the respondent believe health is a first priority?
barplot5 <-
    data %>% ggplot(aes(x = HthyPriority, y = after_stat(count), fill = RecPerExam)) +
    geom_bar(position = 'dodge') +
    labs(x="",
         y="Frequency",
         title = "Do you believe health is a\nfirst priority?",
         fill="Months since\nlast check-up")

# Are check-ups subsidized by the respondent's employer or community?
barplot6 <-
    data %>% ggplot(aes(x = FlwHealth, y = after_stat(count), fill = RecPerExam)) +
    geom_bar(position = 'dodge') +
    labs(x="",
         y="Frequency",
         title = "Does you constantly follow updates your health measures?",
         fill="Months since\nlast check-up")

grid.arrange(barplot1, barplot2, barplot3, barplot4, ncol=2,nrow=2)
grid.arrange(barplot5, barplot6, ncol=2,nrow=2)

rm(barplot1, barplot2, barplot3, barplot4, barplot5, barplot6)
```

# Methods

```{r, echo=FALSE}
# Convert yes/no variables to binary
data$StabHthStt <- ifelse(data$StabHthStt=="yes",1,0)
data$Wstmon <- ifelse(data$Wstmon=="yes",1,0)
data$DiscDisease <- ifelse(data$DiscDisease=="yes",1,0)
data$Lessbelqual <- ifelse(data$Lessbelqual=="yes",1,0)
data$NotImp <- ifelse(data$NotImp=="yes",1,0)
data$HthyPriority <- ifelse(data$HthyPriority=="yes",1,0)
data$FlwHealth <- ifelse(data$FlwHealth=="yes",1,0)
```

```{r,echo=FALSE}
# BIC selection
num_pred_variables <- 7
regfit.full <- regsubsets(RecPerExam ~ StabHthStt + Wstmon + DiscDisease + Lessbelqual + HthyPriority + NotImp + FlwHealth, data = data, nvmax = num_pred_variables, method = "backward")
reg.summary <- summary(regfit.full)
var_num_bic <- which.min(reg.summary$bic)
plot(reg.summary$bic, xlab = "Number of Variables", ylab = "BIC", type = "l")
points(var_num_bic, reg.summary$bic[var_num_bic], col = "red", cex = 2, pch = 20)
coef(regfit.full, var_num_bic)
```

```{r}
# glm code
glm <- glm(as.numeric(RecPerExam) ~ Wstmon + HthyPriority + ComSubsidy,data=data)
```

# Results

# Conclusions
